Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-22 referee.tex
Adjusted some referee responses.

We have performed resolution tests to determine if our results are resolution dependent. The important simulation parameter to see how many stars form within a certain spatial range is called StarClusterCombineRadius. Within our original simulation, this parameter was set to 10 pc, meaning that all stars that would form within 10 pc are merged into a single star. To make sure that resolution does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are resolution independent. This detail has been added to section 2.2.1.

@@

We have compared the mass calculations between Rockstar and Machacek+01 and have found the following results. Figure \ref{fig:compare_mass} shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses. To do this calculation, we calculated the virial mass around the center of each halo given by Rockstar by determining the sphere that contains an average overdensity of 200 $\rho_{c}$. We see that the halos generally fall on a 1:1 relation, ensuring that the two methods are comparable. The halos that have larger calculated masses compared to Rockstar masses are those that are sub-halos. This results in a larger radius at the point where the average overdensity of 200 $\rho_{c}$ falls off, and thus a larger calculated mass. Within our calculations, we do not consider sub-halos, and take the most massive halo the sub-halo falls within for our analysis.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_halo_mass.pdf}
    \label{fig:compare_mass}
\end{figure}

>>>>

There was an error in the original draft of our paper, stating that "If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say "within 10 pc", not "within 1 pc". This error has been corrected.

The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star. To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run. The simulations run for a total of 10 Myr. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are independent of this value. This detail has been added to section 2.2.1.

@@

We have compared the mass calculations between Rockstar and Machacek+01 and have found the following results. Figure \ref{fig:compare_mass} below shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses compare. To do this calculation, we calculated the virial mass around the center of each halo given by Rockstar by determining the sphere that contains an average overdensity of 200 $\rho_{c}$. We see that the halos generally fall on a 1:1 relation, ensuring that the two methods are comparable. The halos that have larger calculated masses compared to Rockstar masses are those that are sub-halos. This results in a larger radius at the point where the average overdensity of 200 $\rho_{c}$ falls off, and thus a larger calculated mass. Within our calculations, we do not consider sub-halos, and take the most massive halo the sub-halo falls within for our analysis.

\begin{figure}
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{images/compare_halo_mass.pdf}
    \label{fig:compare_mass}
\end{figure}
